---
title       : Sales Ticket App
subtitle    : Automatic Sales Ticket Analyis
author      : Iskar Waluyo Moreno
job         : Operations Manager Super Mas Super Market
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## What the application does? 

- This application simplifies studying sales tickets in Super Mas Stores.
- Super Mas stores currently has an average of 147 transactions per day per store. 
- Each transaction creates a unique ticket that can be analyzed. The information can be used to take administrative decisions for the store.
- This application will process the acumulated tickets per month and allow users to proccess the information inmediately as long as the information is up to date.
- The information proccessing will result in 5 useful reports

--- .class #id 
## Data

- Each transaction made in the POS systems is recorded in a server. 
- For the application data from January to December of 2014 is available in the operation. 
- Data is uploaded into a Github account.
    * https://github.com/cheespanther/SMTicketSalesApp/tree/master/datos
- The data is organized in .csv with the following headers: 
    * Time stamp
    * User
    * Total sales
    * Store in which the sale was made

---.class #id 
## Tickets processing
The App will display 5 windows

###  1. Summary by cashier (Resumen Cajeros)
```{r, eval = FALSE}
dataticketsplit <<- split(dataset, dataset$session_id.user_id.display_name)
dataticketsplit2 <<- list2env(dataticketsplit, envir = .GlobalEnv)
```

###  2. Number of tickets by range (Rango Tickets)
```{r, eval = FALSE}
c1 <- as.matrix(subset (soloventas, soloventas <= 20))
c2 <- as.matrix(subset (soloventas, soloventas > 20 & soloventas <= 50))
c3 <- as.matrix(subset (soloventas, soloventas > 50 & soloventas <= 100))
c4 <- as.matrix(subset (soloventas, soloventas > 100 & soloventas <= 200))
c5 <- as.matrix(subset (soloventas, soloventas > 200 & soloventas <= 400))
c6 <- as.matrix(subset (soloventas, soloventas > 400))
```

---.class #id 
## Tickets processing (cont.)
### 3. Sales by cashier graphic
```{r, eval = FALSE}
bwplot(session_id.user_id.display_name~amount_total, data=dataset,
      xlab="Venta Promedio por Ticket",
      ylab="Cajero",
      main="Promedio de Ventas por Ticket")
```

### 4. Summary of tickets (max & min, average, total sales, total tickets)

```{r, eval = FALSE}
promedio_cajeros <<- ddply (dataset, "session_id.user_id.display_name", summarise, 
promediocajero = mean(amount_total))
numero_de_ventas <<- ddply (dataset, "session_id.user_id.display_name", summarise, 
ticketstotal = length(amount_total))
suma_cajeros <<- ddply (dataset, "session_id.user_id.display_name", summarise, 
ventatotal = sum(amount_total))
cajeros <<- cbind(promedio_cajeros, numero_de_ventas[,2], suma_cajeros[,2])
```

---.class #id 
## Uses for these reports 
- The reports provided by this application will allow administrators to easily summarize the general sales information for each month and analyze what kind of customers are walking into the store. 
- This will allow for better decision making when deciding what kinds of new products/services to offer and what kind of design the store should have. 
- Example: customers that purchase less than $50.00 MXN are more than likely convenience shopper and this type of customer has specefice patterns and needs.
- Information will be updated each month. 
- The code will be adjusted to allow selection by month and year. 
